
### Title: CUNY SPS MDS Data_607_Assignment1"
### Author: Charles Ugiagbe
### Date: "8/29/2021"


#### Introduction
This data is about [The Economic Guide to picking a college Major](https://raw.githubusercontent.com/omocharly/DATA-607/main/grad-students.csv)  
The data shows numbers of graduate from different college major and their employment rate
we try to see the employment rate of each college major.


#### Load the required libraries
```{r load library}
library(tidyverse)
```

#### Read Files
This reads the file from github into a tibble (dataframe) and check the head to have an idea of the data
```{r Read Head data}
url <- "https://raw.githubusercontent.com/omocharly/DATA-607/main/grad-students.csv"
grad_students <- read.csv(url)
head(grad_students) # read the file into a tibble
```
##### Columns
Explore the data set to see the names of each columns
```{r Colnames}
colnames(grad_students)
```
#### Structure
Check the Structure of the data
```{r structure}
str(grad_students)
```


```{r}

```

#### Subset the data
Subset the original data "grad_students" by using dplyr
```{r subset}
grad_students_Subset <- select(grad_students, Major_code:Grad_unemployment_rate)
head(grad_students_Subset)
```
#### Check the Summary
Check the descriptive Statistics Summary
```{r Summary}
summary(grad_students)

```


## R Markdown


